\documentclass[11pt]{article}
\usepackage[top=1.5cm,bottom=2cm,left=2cm,right= 2cm]{geometry}
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{amsmath}            
\usepackage{multirow}    
\usepackage{multicol}    
\usepackage{changepage}
\usepackage{lscape}
\usepackage{enumitem}
\usepackage{ulem}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\usepackage{xcolor}

\definecolor{oiB}{rgb}{.337,.608,.741}
\definecolor{oiR}{rgb}{.941,.318,.200}
\definecolor{oiG}{rgb}{.298,.447,.114}
\definecolor{oiY}{rgb}{.957,.863,0}

\definecolor{light}{rgb}{.337,.608,.741}
\definecolor{dark}{rgb}{.337,.608,.741}

\usepackage[colorlinks=false,pdfborder={0 0 0},urlcolor= dark,colorlinks=true,linkcolor=black]{hyperref}

\newcommand{\light}[1]{\textcolor{light}{\textbf{#1}}}
\newcommand{\dark}[1]{\textcolor{dark}{#1}}
\newcommand{\gray}[1]{\textcolor{gray}{#1}}



%\date{}                                           % Activate to display a given date or no date

%

\begin{document}

{\LARGE \textcolor{oiB}{Learning Objectives \hfill Chapter 4: Distributions of random variables}} \\

\begin{enumerate}
\renewcommand\labelenumi{\textcolor{oiB}{\textbf{LO \theenumi.}}}

\item Define the standardized (Z) score of a data point as the number of standard deviations it is away from the mean: $Z = \frac{x - \mu}{\sigma}$.

\item Use the Z score 
\begin{itemize}
\item[-] if the distribution is normal: to determine the percentile score of a data point (using technology or normal probability tables)
\item[-] regardless of the shape of the distribution: to assess whether or not the particular observation is considered to be unusual (more than 2 standard deviations away from the mean) 
\end{itemize}

\item Depending on the shape of the distribution determine whether the median would have a negative, positive, or 0 Z score.

\item Assess whether or not a distribution is nearly normal using the 68-95-99.7\% rule or graphical methods such as a normal probability plot.

\end{enumerate}

\gray{
{\it
\vspace{-0.75cm}
\begin{itemize}
\renewcommand{\labelitemi}{{\textcolor{oiB}{$\ast$}}}
\item Reading: Section 4.1 of Advanced High School Statistics
\item Video: \href{http://www.youtube.com/watch?v=ev463hHe544}{Normal Distribution - Finding Probabilities - Dr.\c{C}etinkaya-Rundel, YouTube, 6:04}
\item Video: \href{http://www.youtube.com/watch?v=6rAg4Y6NirU}{Normal Distribution - Finding Cutoff Points - Dr.\c{C}etinkaya-Rundel, YouTube, 4:25}
\item Additional resources:
\begin{itemize}
\item Video: \href{http://www.youtube.com/watch?v=McSFVzc8Swk&list=PL568547ACA9211CCA&index=24}{Normal distribution and 68-95-99.7\% rule, YouTube, 3:18}
\item Video: \href{http://www.youtube.com/watch?v=5v3Czc6ZK-Q&list=PL568547ACA9211CCA&index=23}{Z scores - Part 1, YouTube, 3:03} 
\item Video: \href{http://www.youtube.com/watch?v=aa_deKPDgI4&list=PL568547ACA9211CCA&index=22}{Z scores - Part 2, YouTube, 4:01}
\end{itemize}
\item Test yourself: True/False: In a right skewed distribution the Z score of the median is positive.
\end{itemize}
}}

%

\vspace{0.48cm}
\begin{enumerate}[resume]
\renewcommand\labelenumi{\textcolor{oiB}{\textbf{LO \theenumi.}}}
\item Calculate the sampling variability of the mean, the standard deviation of the sample mean, as $SD_{\bar{x}} = \frac{\sigma}{\sqrt{n}}$, where $\sigma$ is the population standard deviation.

\item Recognize that the Central Limit Theorem (CLT) tells us about the \textit{shape} of the sampling distributions, and that given certain conditions, the distribution of the sample mean will be nearly normal.
\begin{itemize}
\item[-] In the case of the mean the CLT tells us that if
\begin{itemize}[parsep=0pt]
\item[(1a)] the sample size is sufficiently large $(n \ge 30)$ or
\item[(1b)] the population is known to have a normal distribution
\end{itemize}
then the distribution of the sample mean will be nearly normal, centered at the true population mean and with a standard deviation of $\frac{\sigma}{\sqrt{n}}$.
\item[-] The larger the sample size ($n$), the less important that the shape of the original distribution becomes, i.e. when $n$ is very large the sampling distribution will be nearly normal regardless of the shape of the population distribution.
\end{itemize}
\item Carry out probability calculations involving a sample mean by first checking that conditions for a normal distribution are met and them performing normal approximation, using the correct standard deviation in the denominator of the Z-score.
\end{enumerate}


\gray{
{\it
\vspace{-0.5cm}
\begin{itemize}
\renewcommand{\labelitemi}{{\textcolor{dark}{$\ast$}}}
\item Reading: Section 4.2 of Advanced High School Statistics
\item Videos: 
\begin{itemize}
\item \href{http://www.youtube.com/watch?v=dF18I7-Re4I}{Sample vs. sampling distribution, Dr. \c{C}etinkaya-Rundel} (9:30)
\item \href{http://www.youtube.com/watch?v=Cvc8sYAKmtI}{Working with the CLT for means, Dr. \c{C}etinkaya-Rundel} (3:16)
\item \href{http://www.youtube.com/watch?v=j4ZpJ0T6eFw&feature=autoplay&list=PL568547ACA9211CCA&playnext=1}{Distribution of the sample mean, YouTube} (6:17)
\item \href{http://www.khanacademy.org/math/statistics/v/central-limit-theorem}{Central Limit Theorem, Khan Academy} (9:49)
\item \href{http://www.khanacademy.org/math/statistics/v/sampling-distribution-of-the-sample-mean}{Sampling Distribution of the Mean, Khan Academy} (10:52)
\end{itemize}
\item Test yourself: 
{\small
\begin{enumerate}
\item Suppose heights of all men in the US have a mean of 69.1 inches and a standard deviation of 2.9 inches. Would a randomly selected man who is 72 inches tall be considered unusually tall? Would it be unusual to have a random sample of 100 men where the sample average is 72 inches?
\end{enumerate}
}
\end{itemize}
}}



\vspace{0.48cm}
%

\begin{enumerate}[resume]
\renewcommand\labelenumi{\textcolor{oiB}{\textbf{LO \theenumi.}}}

%\item Determine if a random variable is binomial using the four conditions:
%\begin{itemize}
%\item[-] The trials are independent. 
%\item[-] The number of trials, n, is fixed. 
%\item[-] Each trial outcome can be classified as a success or failure. 
%\item[-] The probability of a success, p, is the same for each trial. 
%\end{itemize}
%
%\item Calculate the number of possible scenarios for obtaining $k$ successes in $n$ trials using the choose function: ${n \choose k} = \frac{n!}{k!~(n - k)!}$.
%
%\item Calculate probability of a given number of successes in a given number of trials using the binomial distribution: $P(k = K) = \frac{n!}{k!~(n - k)!}~p^k~(1-p)^{(n - k)}$. 
\item Determine if a random variable follows a binomial distribution.  Recall from Chapter 3 that a variable is binomial if the following four conditions are met:
\begin{itemize}
\item[-] The trials are independent. 
\item[-] The number of trials, n, is fixed. 
\item[-] Each trial outcome can be classified as a success or failure. 
\item[-] The probability of a success, p, is the same for each trial. 
\end{itemize}

\item Calculate the probabilities of the possible values of a binomial random variable using the binomial formula.  Recall that the sum of the probabilities must add to 1.

\item Calculate the expected number of successes in a given number of binomial trials $(\mu = np)$ and its standard deviation $(\sigma = \sqrt{np(1-p)})$.

\item When number of trials is sufficiently large ($np \ge 10$ and $n(1-p) \ge 10$), use normal approximation to calculate binomial probabilities, and explain why this approach works.

\end{enumerate}



\gray{
{\it
\vspace{-0.75cm}
\begin{itemize}
\renewcommand{\labelitemi}{{\textcolor{oiB}{$\ast$}}}
\item Reading: Section 4.4 of Advanced High School Statistics
\item Video: \href{http://www.youtube.com/watch?v=tKmyzhvgudw}{Binomial Distribution - Finding Probabilities - Dr.\c{C}etinkaya-Rundel, YouTube, 8:46}
\item Additional resources:
\begin{itemize}
\item Video: \href{http://www.youtube.com/watch?v=oYeJBdCGwxk&list=PL568547ACA9211CCA&index=28&feature=plpp_video}{Binomial distribution, YouTube, 4:25}
\item Video: \href{http://www.youtube.com/watch?v=0er3EiM-bpg&list=PL568547ACA9211CCA&index=27&feature=plpp_video}{Mean and standard deviation of a binomial distribution, YouTube, 1:39} 
\end{itemize}
\item Test yourself: 
\begin{enumerate}
\item True/False: We can use the binomial distribution to determine the probability that in 10 rolls of a die the first 6 occurs on the 8th roll.
\item True / False: If a family has 3 kids, there are 8 possible combinations of gender order.
\item True/ False: When $n = 100$ and $p = 0.92$ we can use the normal approximation to the binomial to calculate the probability of 90 or more successes.
\end{enumerate}
\end{itemize}
}}

%

\vspace{0.48cm}
\begin{enumerate}[resume]
\renewcommand\labelenumi{\textcolor{oiB}{\textbf{LO \theenumi.}}}
\item Recognize that the sample proportion, $\hat{p}$, has a distribution and that its distribution is centered on the true population proportion, $p$.
\item Calculate the sampling variability or standard deviation of the sample proportion, as \\$SD_{\hat{p}} = \sqrt{\frac{\hat{p}(1-\hat{p})}{n}}$.
\item Recognize that the Central Limit Theorem (CLT) tells us about the \textit{shape} of the sampling distributions, and that given certain conditions, the distribution of the sample proportion will be nearly normal, specifically when $np\ge 10$ and $n(1-p)\ge 10$.
\item Carry out probability calculations involving a sample proportion by first checking that conditions for a normal distribution are met and them performing normal approximation, using the correct standard deviation in the denominator of the Z-score.
\end{enumerate}


\gray{
{\it
\vspace{-0.5cm}
\begin{itemize}
\renewcommand{\labelitemi}{{\textcolor{dark}{$\ast$}}}
\item Reading: Section 4.5 of Advanced High School Statistics
\item Test yourself: 
{\small
\begin{enumerate}
\item Suppose 45\% of voters in a particular county favor a proposition for an increase in property tax.  If a researcher takes a random sample of 40 people, what is the probability that greater than 50\% of the sample will favor the proposition (thus leading the researcher to incorrectly believe that more than half of the voters are in favor)?  
\end{enumerate}
}
\end{itemize}
}}

\end{document}